\hrule\hrule\bigskip\bigskip A simple and efficient algorithm for computing approximate Nash equilibria in two-person zero-sum games with imcomplete information

### 2015-06-07 nips2015.tex
glitches + fixups
refactor algorithm listing in tex

The above definition is a generalization of the notion of Nash
equilibria in the sense that
\begin{itemize}
\item Exact Nash equilibria correspond to Nash $(0^+,0^+)$-equilibria.
\item Nash $\epsilon$-equilibria (in the sense of Definition
  \ref{thm:approx_nash}) correspond to Nash $(0^+,\epsilon)$-equilibria.
\end{itemize}

\subsection{The algorithm proper and its convergence rate}
Consider the following algorithm for solving the GSP
\eqref{eq:unconstrained_pb}
\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\rho >0$, $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$.
\Ensure A Nash $(\rho, \epsilon)$-equilibrium
$(\tilde{y},\tilde{p},\tilde{x},\tilde{q}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$,
$\tilde{v}_a^{(0)} \leftarrow 0$, $k \leftarrow 0$
\While{$\|\tilde{\epsilon}_a^{(k)}\| \ge \rho$ or
  $\|\tilde{v}_{a}^{(k)}\| \ge \epsilon$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$
\State  \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$
\State  \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} +
\lambda(E_2y^{(k+1)}-e_2)$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda
(A^T(x^{(k+1)}-x^{(k)}) + E_2^T(q^{(k+1)}-q^{(k)}))$
\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda
E_1(x^{(k+1)}-x^{(k)})$
\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k} +
\frac{1}{\lambda}(y^{(k+1)}-y^{(k)},p^{(k+1)}-p^{(k)},x^{(k+1)}-x^{(k)},q^{(k+1)}-q^{(k)})$
\State $\tilde{v}_a^{(k+1)} \leftarrow \frac{1}{k + 1}v_a^{(k+1)}$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

\begin{theorem}[Ergodic $\mathcal{O}(1/k)$ convergence]
Let $d_0$ be the euclidean distance between the starting point
$(y^{(0)},p^{(0)},x^{(0)},q^{(0)})$ of Algorithm \ref{Tab:algo} and the
set of equilibria for the GSP \eqref{eq:unconstrained_pb}.
Then given any $\epsilon > 0$ and $\rho > 0$, there exists and index
$k_0 \le 2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ such that the following
error bounds hold:
\begin{eqnarray}
\|\tilde{\epsilon}^{a}_{k_0}\| \le \rho\text{ and }\|\tilde{v}^{a}_{k_0}\| \le
\epsilon.
\end{eqnarray}

Thus Algorithm \ref{Tab:algo} outputs an $(\rho,\epsilon)$-Nash
Equilibrium for the GSP \eqref{eq:unconstrained_pb}
in at most $2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ iterations.
\end{theorem}

@@

$E_1 \in \mathbb{E}^{3 \times 5}$ with $E_1(0,0) = E_1(1,1) =
E_1(1,2) = E_1(2,3) = E_1(2,4) = \textbf{1}$,
$E_1(1,0) = E_1(2,0) = \textbf{-1}$; \\

$E_2 \in \mathbb{E}^{3 \times 5}$ with $E_2(0,0) = E_2(1,1) = E_2(1,2)
= E_2(2,3) = E_2(2,4) = \textbf{1}$, $E_2(1,0) = E_2(2,0) =
\textbf{-1}$; and \\

$A \in \mathbb{E}^{5 \times 5}$ with $A(2,0) =
A(4,0) = \textbf{-0.5}$, $A(1,3) = \textbf{1}$, $A(3,1) =
\textbf{-1}$, $A(1,2) = A(1,4) = A(3,2) = A(3,4) = \textbf{0.25}$.

@@

$E_1 \in \mathbb{E}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
E_1(6,11) = \textbf{1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
E_1(5,5) = E_1(6,9) = \textbf{-1}$; \\

 $E_2 \in \mathbb{E}^{7 \times 13}$
$E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
E_2(6,4) = \textbf{1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
E_2(5,0) = E_2(6,0) = \textbf{-1}$; and \\

 $A \in \mathbb{E}^{13 \times
  13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
\textbf{-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
A(6,4) = A(6,12) = A(10,4) = A(10,8) = \textbf{-0.166667}$, $A(7,4) =
A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = \textbf{0.333333}$,
$A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
A(12,1) = A(12,5) = \textbf{0.166667}$.\\

>>>>

The above definition is a generalization of the notion of Nash
equilibria since:
\begin{itemize}
\item Exact Nash equilibria correspond to Nash $(0^+,0^+)$-equilibria.
\item Nash $\epsilon$-equilibria (in the sense of Definition
  \ref{thm:approx_nash}) correspond to Nash $(0^+,\epsilon)$-equilibria.
\end{itemize}

\subsection{Algorithm and convergence rate}
Consider the following algorithm for solving the GSP
\eqref{eq:unconstrained_pb}
\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\rho >0$, $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$.
\Ensure A Nash $(\rho, \epsilon)$-equilibrium
$({y^*},{p^*},{x^*},{q^*}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$, $k \leftarrow 0$
\While{$\|\tilde{\epsilon}_a^{(k)}\| \ge \epsilon$ or
  $\|{v}_{a}^{(k)}\|/k \ge \rho$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$
\State  $p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$
\State $\Delta x^{(k+1)} \leftarrow x^{(k+1)}-x^{(k)}$
\State $\Delta q^{(k+1)} \leftarrow q^{(k+1)}-q^{(k)}$
\State  $q^{(k+1)} \leftarrow q^{(k)} + \Delta q^{(k+1)}$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda (A^T\Delta x^{(k+1)}
+ E_2^T\Delta q^{(k+1)})$
\State $\Delta y^{(k+1)} \leftarrow y^{(k+1)}-y^{(k)}$
\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1\Delta x^{(k+1)}$
\State $\Delta p^{(k+1)} \leftarrow p^{(k+1)}-p^{(k)}$
\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k)} + \frac{1}{\lambda}(\Delta
y^{(k+1)},\Delta p^{(k+1)},\Delta x^{(k+1)},\Delta q^{(k+1)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

\begin{theorem}[Ergodic $\mathcal{O}(1/k)$ convergence]
Let $d_0$ be the euclidean distance between the starting point
$(y^{(0)},p^{(0)},x^{(0)},q^{(0)})$ of Algorithm \ref{Tab:algo} and the
set of equilibria for the GSP \eqref{eq:unconstrained_pb}.
Then given any $\epsilon > 0$ and $\rho > 0$, there exists and index
$k_0 \le 2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ such that the following
error bounds hold:
\begin{eqnarray}
\|\tilde{v}_a^{k_0}\| \le \rho \text{ and }
\|\tilde{\epsilon}_a^{k_0}\| \le \epsilon
\end{eqnarray}

where $\tilde{v}_a^{(k_0)} := v_a^{(k_0)}/k_0$.
Thus Algorithm \ref{Tab:algo} outputs an $(\rho,\epsilon)$-Nash
equilibrium for the GSP \eqref{eq:unconstrained_pb}
in at most $2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ iterations.
\end{theorem}

@@

$E_1 \in \mathbb{R}^{3 \times 5}$ with $E_1(0,0) = E_1(1,1) =
E_1(1,2) = E_1(2,3) = E_1(2,4) = \textbf{1}$,
$E_1(1,0) = E_1(2,0) = \textbf{-1}$; \\

$E_2 \in \mathbb{R}^{3 \times 5}$ with $E_2(0,0) = E_2(1,1) = E_2(1,2)
= E_2(2,3) = E_2(2,4) = \textbf{1}$, $E_2(1,0) = E_2(2,0) =
\textbf{-1}$; and \\

$A \in \mathbb{R}^{5 \times 5}$ with $A(2,0) =
A(4,0) = \textbf{-0.5}$, $A(1,3) = \textbf{1}$, $A(3,1) =
\textbf{-1}$, $A(1,2) = A(1,4) = A(3,2) = A(3,4) = \textbf{0.25}$.

@@

$E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
E_1(6,11) = \textbf{1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
E_1(5,5) = E_1(6,9) = \textbf{-1}$; \\

 $E_2 \in \mathbb{R}^{7 \times 13}$
$E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
E_2(6,4) = \textbf{1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
E_2(5,0) = E_2(6,0) = \textbf{-1}$; and \\

 $A \in \mathbb{R}^{13 \times
  13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
\textbf{-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
A(6,4) = A(6,12) = A(10,4) = A(10,8) = \textbf{-0.166667}$, $A(7,4) =
A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = \textbf{0.333333}$,
$A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
A(12,1) = A(12,5) = \textbf{0.166667}$.\\
